New lower bounds for Schur and weak Schur numbers

### 2021-06-20 article/weakschur.tex
reformulation en terme de templates de la demo WS > 3/2 WS

\begin{remark}
The inequality from \hyperref[Corollary3.2]{Corollary 3.2} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
odd in the theorem). However, it makes the proof less clear and it is never useful in practice.
\end{remark}

@@

\begin{itemize}
\item \(\forall i \in [\![1, n]\!], A_i\) is weakly-sum-free,
\item \(\forall i \in [\![1, n]\!], A_i\backslash [\![1, b]\!]\) is sum-free,
\item For \(A_n\) (the special subset) :
	\[
	\forall (x,y) \in A_n^2, \,x+y>b+2a \implies x+y-2a\notin A_n,
	\]
\item For the others subsets
	\[
	\forall i \in [\![0,n-1]\!], \, \forall(x,y) \in A_i^2, \, x+y>a+b \implies \pi(x+y) \notin A_i.
	\]
\end{itemize}
\end{definition}

@@

There is a construction theorem for S-templates as well.

@@

\begin{proof}[\textsc{Proof of \hyperref[Theorem3.1]{Theorem 3.1}.}]
\label{PreuveThm}
\textbf{REFORMULER LA PREUVE EN TERMES DE WS-TEMPLATES.} \\
\end{proof}

>>>>

\begin{remark}
The inequality from \hyperref[Corollary3.2]{Corollary 3.2} can be improved by adding 1 to the lower bound if \(\WS (n)\) is odd (more generally if \(q\) is
odd in the theorem). However, it lengthens the proof and it is never useful in practice.
\end{remark}

@@

\begin{itemize}
\item \(\forall i \in [\![1, n]\!], A_i\) is weakly-sum-free,
\item \(\forall i \in [\![1, n]\!], A_i\backslash [\![1, b]\!]\) is sum-free,
\item For \(A_n\) (the special subset) :
	\[
	\forall (x,y) \in A_n^2, \,x+y>b+2a \implies x+y-2a\notin A_n,
	\]
\item For the others subsets
	\[
	\forall i \in [\![1,n-1]\!], \, \forall(x,y) \in A_i^2, \, x+y>a+b \implies \pi(x+y) \notin A_i.
	\]
\end{itemize}
\end{definition}

@@

There is a construction theorem for WS-templates as well.

@@

\begin{proof}[\textsc{Proof of \hyperref[Theorem3.1]{Theorem 3.1}.}]
\label{PreuveThm}
Let \((q, n) \in (\mathbb{N}^*)^2\) such that there exists a partition of \([\![1, q]\!]\) into n weakly sum-free subsets. 
Let \(f: [\![1, q]\!] \rightarrow [\!]1, n]\!]\) a weakly sum-free colouring.
Let \(b=q\) and \(a = q + \left \lceil \dfrac{q}{2} \right \rceil + 1\). A new colouring \(g\) is defined as follows:

\[
\begin{array}{c c c l}
	g : & [\![1, a + b]\!] & \longrightarrow & [\![1, n + 1]\!] \\
	& x & \longmapsto &
		\left\{ \begin{array}{l l}
			f(x) & \text{if}~x \in [\![1, b]\!]  \\
			n + 1 & \text{if}~x \in [\![b + 1, 2 b + 1]\!] \\
			f(x - a) & \text{if}~x \in  [\![2 b + 2, a + b]\!]
		\end{array} \right.
\end{array}
\]

We claim that \(g\) is a \(b\)-WSF-template with width \(a\) and \(n + 1\) colours.

\begin{itemize}
\item Function \(g_{|[\![b + 1, a + b]\!]}\) is a sum-free colouring. Indeed, let \((x, y) \in 
	[\![b + 1, a + b]\!]^2\) such that \(g(x) = g(y)\). If \(g(x) = n + 1\) then \(z = x + y > 2 b + 1\) 
	and therefore, either \(z > a + b\) or \(f(z) \neq n + 1\). Otherwise, \(x + y > a + b\).
\item Function \(g\) is a weakly sum-free colouring. Indeed, let \((x, y) \in [\![1, a + b]\!]^2\) such that 
	\(z = x + y \leqslant a + b\) and \(g(x) = g(y)\). Given that \(x\) and \(y\) have symmetric roles, 
	we can assume that \(x \leqslant y\). If \(x > b\) then \(g(z) \neq g(x)\) as seen above. If \(y \leqslant b\) then 
	\(f(x) = g(x) = g(y) = f(y) \leqslant n\) and either \(z \leqslant a + b\) and \(f(z) \neq f(x)\) since \(f\) is a weakly 
	sun-free colouring or \(a + b + 1 \leqslant z \leqslant 2 b\) and \(g(z) = n + 1\); therefore \(g(z) \neq g(x)\). If 
	\(x \leqslant b\) and \(y > b\) then \(g(x) = f(x)\), \(g(y) = f(y - a)\) and \(g(z) = f(z - a)\).We have \(x \neq y - a\) 
	(otherwise, we would have \(a + b \geqslant z = 2 y  - a \geqslant 4 b + 4 - a > a + b\)) and thus \(f(x + y - a) \neq f(x)\),
	that is \(g(z) \neq g(x)\).
\item Colour \(n + 1\) verifies the additionnal constraints for the special colour. Indeed, \(b + 2 a \geqslant 4 b + 2\). 
	Hence, \(\forall (x, y) \in g^{-1}(\{n + 1\}), x + y \leqslant b + 2 a\).
\item Colours \(1, ..., n\) verify the additionnal constraints for the regular colours. Indeed, let 
	\((x, y) \in g^{-1}([\![1, n]\!])\) such that \(x + y > a + b\). Given that \(x\) and \(y\) have symmetric roles, 
	we can assume that \(x \leqslant y\). Necessarily \(y \geqslant 2 b + 2\). If \(x \leqslant b\) then 
	\(z = x + y \in [\![a + b + 1, a + 2 b]\!]\) and therefore \(\pi(z) \in [\![b + 1, 2 b]\!]\). Otherwise, 
	\(z = x + y \in [\![4 b + 4, 2 a + 2 b]\!]\) and therefore \(\pi(z) \in [\![b + 1, 2 b]\!]\). Hence, in both cases, 
	\(g(\pi(z)) \neq g(x)\).
\end{itemize}

The result is then obtained by applying \hyperref[Theorem3.18]{Theorem 3.18}. \\
\end{proof}
